% Fundamental postulates of quantum mechanics.
\subsection{The postulates of quantum mechanics}
Let us begin by recapitulating the postulates of quantum mechanics. Depending on what literature you are looking at, a different number of postulates will be listed [Shankar\cite{Shankar}, Griffiths\cite{griffiths:quantum}, Laurent Nottale\cite{Nottale:2007ne}]. However, let us start by looking at those which count as the most fundamental ones, and expand upon them\footnote{If one wants to, there are actually three subsets of postulates in QM[see laurent nottale], the fundamental ones, the secondary ones which can be derived from the fundamental ones, and the principles which are more consequences of the fundamental ones.}.

\begin{enumerate}[I]
	\item \textit{Complex state function.} The state of a quantum mechanical system can be described by a complex valued vector, $\ket{\psi}$ that lives in Hilbert space $\mathcal{H}$. Vectors in Hilbert space is often referred to as states.
	\item \textit{The correspondence principle.} A physical observable has an Hermitian operator. For every dynamical variable in classical mechanics, there is a corresponding quantum mechanical one. Further, the principle states we reproduce the classical results in the limit of large quantum numbers. Further, on order to convert to from classical to quantum mechanics, we replace the Poisson brackets with the the commutator ones divided by $i\hbar$.
	\begin{align}
		\{\cdot,\cdot\} \rightarrow \frac{1}{i\hbar}[\cdot,\cdot]
		\label{eq:poisson}
	\end{align}
	Further, any observable $\hat{\Omega}$ measured will result in a eigenvalue $\omega$ associated with the observable. These are related through the equation eigenvalue equation, $\hat{\Omega}\ket{\psi}=\omega\ket{\psi}$
	\item \textit{Von Neumann's postulate(collapse of state).} If we measure a system $\ket{\psi}$ with an observable $\Lambda$ and get the eigenvalue of $\omega_i$, then the system will be in a state $\ket{\psi_i}$ after the measurement\footnote{A measurement is here an ideal experiment which we minimally disturb the system and it is in compliance with theory. In classical mechanics, an ideal measurement is a measurement in which the system remains unaffected.}. We say that the system has \textit{collapsed} into state $\ket{\psi_i}$.
	\item \textit{The Schröedinger equation.} We require a state vector $\ket{\psi(t)}$ to abide by the Schröedinger equation,
	\begin{align}
		i\hbar\frac{d}{dt}\ket{\psi(t)} = \hat{H} \ket{\psi(t)}
		\label{eq:schroedinger}
	\end{align}
	where the Hamiltonian $\hat{H}$ is a linear Hermitian operator constructed accordingly to the correspondence principle.
	\item \textit{Born's postulate.} The wave function squared $|\psi|^2$ is interpreted as a the probability of the system at a given configuration. For instance, the Probability of getting the eigenvalue $\omega_i$ in a state $\ket{\psi}$ is given by $|\langle\omega_i|\psi\rangle|^2$. This implies that the wave function must be normalized,
	\begin{align}
		\langle \psi | \psi \rangle = 1
		\label{eq:wf-normalized}
	\end{align}
\end{enumerate}
From these postulates follow several other properties and consequences.

\subsection{Formalism of Quantum mechanics}
As alluded to in the postulates, the quantum mechanical world is on of vectors and Hilbert spaces. The rules of this game are built on top of properties that follows from the Hilbert space.

\subsubsection{Superposition principle}
Applying the superposition principle in quantum mechanics, we get from the linearity of the Hamiltonian $\hat{H}$ in the Schröedinger equation \eqref{eq:schroedinger} that a quantum mechanical state is built up from a set of linear independent states. Given vectors $\ket{u},\ket{w} \in \mathcal{H}$(which are our wave functions) and complex numbers $\alpha,\beta$, we have that $\mathcal{H}$ is closed under addition and multiplication with scalars,
\begin{align}
	\ket{w} = \alpha\ket{u} + \beta\ket{v} \in \mathcal{H}
	\label{eq:hilbert_linearity}
\end{align}

\subsubsection{Adjoint operator}
Further, we have that the inner product maps the vectors to complex numbers. From this we have the property of complex conjugate operators,
\begin{align}
	\bra{u}v\rangle = \bra{v}u\rangle^*
	\label{eq:complex_conjugate}
\end{align}
The inner product also adheres to the distributive property of complex numbers,
\begin{align}
	\bra{w}\alpha u + \beta v\rangle = \alpha\bra{w}u\rangle + \beta\bra{w}v\rangle
	\label{eq:distributive_property}
\end{align}

\subsubsection{Expansion in eigenfunctions}
A state $\ket{u}$ can be expanded in a basis of eigenfunctions $\ket{u_n} \in \mathcal{H}$ as
\begin{align}
	u = \sum_n c_n \ket{u_n}
	\label{eq:eigenfunction-expansion}
\end{align}
We demand orthogonality form this set, such that 
\begin{align}
	\bra{u_n}v_m\rangle = \delta_{nm}
	\label{eq:eig-func-orthogonality}
\end{align}

\subsubsection{Completeness relation}
The unit operator $\mathrm{1}$ is given by
\begin{align}
	\mathrm{1} = \sum_n \ket{u_n} \bra{u_n}
	\label{eq:unit-operator}
\end{align}

\subsection{Operators}
An operator will map a vector $\ket{u}$ in Hilbert space onto another vector in Hilbert space,
\begin{align}
	\ket{u} \in \mathcal{H} \rightarrow \hat{\Omega}\ket{u} \in \mathcal{H}
	\label{eq:operator-mapping}
\end{align}
The adjoint operator is defined by
\begin{align}
	\bra{u}\hat{\Omega}\ket{v} = \bra{v}\hat{\Omega}^\dagger\ket{u}^*
	\label{eq:adjoint-operator}
\end{align}
An operator is \textit{self-adjoint} or \textit{Hermitian} if $\hat{\Omega}^\dagger = \hat{\Omega}$.

\subsubsection{Eigenvectors and eigenvalues}
The egeinvector(or eigenstate) of an operator $\ket{u}$ is given by
\begin{align}
	\hat{\Omega}\ket{u} = \lambda \ket{u}
	\label{eq:}
\end{align}
with $\lambda$ being a complex number and the eigenvalue.

\subsubsection{Expectation values}
Given some observable $\hat{\Omega}$ and a system described by a normalized wave function $\psi$, we have that the expectation value of that is given as the mean value from statistics.
\begin{align*}
	\langle \Omega \rangle &= \sum_i P(\omega_i) \omega_i = \sum_i |\bra{\omega_i}\psi\rangle|^2\omega_i \\
	&= \sum_i \bra{\psi}\omega_i\rangle \langle\omega_i \ket{\psi} \omega_i \\
	&= \sum_i \bra{\psi} \omega_i \ket{\omega_i} \langle\omega_i \ket{\psi} \\
	&= \sum_i \bra{\psi} \hat{\Omega} \ket{\omega_i} \langle\omega_i \ket{\psi} \\
	&= \bra{\psi} \hat{\Omega} \cdot I \ket{\psi} \\
\end{align*}
We used that $I = \sum_i \ket{\omega_i}\bra{\omega_i}$ and that the $\omega_i\ket{{\omega_i}} = \hat{\Omega}\ket{\omega_i}$. This gives us the expression for the expectation value,
\begin{align}
	\expect{\Omega} = \bra{\psi} \hat{\Omega} \ket{\psi}
	\label{eq:expectation-value}
\end{align}

\subsection{Probability interpretation}
The probability for finding a particle at a position $x$(assume we are in position space) is given by a function $|\psi(x)|^2$, probability per unit length. This is called the \textit{probability density}. The \textit{probability amplitude} is given by $\psi(x)$. The probability for finding the particle between two positions $x_1$ and $x_2$ is given by $\int^{x_2}_{x_1}|\psi(x)|^2dx$. The probability of finding a particle at position $x$ over a series of experiments is given by $\langle\psi|x|\psi\rangle = \int^\mathrm{R} \psi^*(x)x\psi(x)dx$.
